


## Getting a token

```{r eval=FALSE}
account_name <- "statprep.annie@gmail.com"
# Authorize use of the google account
where <- "raw"
whence <- dir(system.file(where, package = "basket"), full.names = TRUE)
whither <- tempdir()
file.copy(whence, whither)
googledrive::drive_auth(cache = whither, use_oob = TRUE,
                        email = account_name)
# Authorize use of the sheets themselves
googlesheets4::gs4_auth(token = googledrive::drive_token())
#unlink(whither)
```


Create a new sheet. The returned object will have the ID for the sheet.
```{r eval = FALSE}
new_sheet <- sheets_create("scared-rabbit4", sheets = head(mtcars))
```

Google sent me back this to give R to produce the token
`4/0gEwuMNKJL2QUJ9tqJv9Bo40qNe3AaMZm9PY5cXTS9sdgRROqxy02WI`

Key to the spreadsheet I created to try things out



```{r eval=FALSE}
library(googlesheets4)

my_sheet_key <- "1w3fEld2rZlR_6FuzvkA-viOLBA5JdqD3xHl-LuLX3-Y"
my_sheet <- googlesheets4::sheets_get(my_sheet_key) # get's metadata
contents <- googlesheets4::read_sheet(my_sheet)
this_event <- tibble::tribble(
  ~ time, ~ content,
  date(), "How now brown cow."
)
sheets_append(this_event, my_sheet)
```



# googledrive::drive_auth(cache=".secrets", use_oob = TRUE,
#                         email = account_name)
# password_df <- suppressMessages(googlesheets4::read_sheet(credentials))
